mir\_eval

### 2014-05-06 paper/paper.tex
Cap

mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{f-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.

>>>>

mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.
